---
title: "Assignment 03 Solution"
author: "(fill in your name)"
output:
  html_document:
    df_print: kable
    theme: simplex
    toc: true
    urlcolor: blue
    toc_float:
      collapsed: false
      smooth_scroll: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Assignment Directions

This file contains an assignment.  Please read the text and adjust the necessary code chunks (between \`\`\` symbols), to accomplish the stated goal.  This assignment is to be completed by each student, no digital sharing is allowed.  Concepts may be discussed, yet submission much be completed by submitting student.

## Bond Portfolio

### Loan Bond Portfolio

For this assignment we wish to load AGG_holdings_Clean.csv from the data directory.

```{r BondPortfolio}

my_file       <- ___
bondPortfolio <- ___

head(bondPortfolio)
# View(bondPortfolio)

```


### Sum Market Value

What is the market value of the portfolio in millions

```{r MarketValue}

mvMil <- ___

print(mvMil)
```


## Submission

Submit the single html file "assignment03.html", Blackboard may require that you zip it prior to submission.  Leave the session info that follows for debugging purposes for the instructor.


## Session Info

```{r}
devtools::session_info()
```

```{r}
date()
sessionInfo()
```

```{r}
date()
Sys.getenv()
```


