---
title:  "Minimum Working Example - 10B"
author: "Larry Tentor"
date:   "4/8/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Sample Data - DateTime

```{r sampleData}
sampleDateTime <- read.csv(stringsAsFactors = FALSE, text = 'DateTime
2007-08-26 19:09:29.263000000
2014-02-27 08:28:07.900000000
2007-01-05 15:00:47.090000000
2012-10-22 11:02:35.010000000
2013-09-14 18:38:39.097000000')

sampleDateTime
```


## Date Time Example {.tabset .tabset-pills}

### Date Only - Purge Time

If you can accept the date only losing the time you may use this.

```{r ConvertDate}

DateSet <- as.Date(sampleDateTime$DateTime)
DateSet

class(DateSet)
```

### Date Time in base R

If you require the full date time you may use a different conversion function; yet this leaves it in character type.

```{r ConvertDateTime}
DateTimeSet <- strftime(sampleDateTime$DateTime)
DateTimeSet

class(DateTimeSet)
```

### Date Time extra package

I'd suggest another package that deals with just this type of datetime more extensively if necessary for properly dealing with datetime values.

```{r LubridatePackage}
#install.packages("lubridate")
library(lubridate)
DateTimeSet2 <- parse_date_time(sampleDateTime$DateTime, orders = c("ymd HMS"))
DateTimeSet2

class(DateTimeSet2)
```

