---
title: "Exercise 03-A Solution"
author: "(fill in your name)"
output:
  html_document:
    df_print: kable
    theme: simplex
    toc: true
    urlcolor: blue
    toc_float:
      collapsed: false
      smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#install.packages(tvm)
library(FinancialMath)
```

## Exercise Directions

This file contains an exercise.  Please read the text and adjust the necessary code chunks (between \`\`\` symbols), to accomplish the stated goal.

## Time Value of Money

### Future Value

You can save $5,000 per year for the next 5 years in an account earning 8 percent per year. How much will you have at the end of the fifth year if you make the first deposit today?

```{r FutureValue}

FV <- ___

FV
```


### Yield to Maturity

A US Treasury bond today trades at $101.1, for a $100 face value payable in two years.  The coupon rate is 3% payable semi-annual.  What is the yield to maturity?

```{r YTM, echo=TRUE}
library(FinancialMath)
face       <- 100
price      <- ___
rateCoupon <- ___
cashCoupon <- ___


cashFlow   <- c(cashCoupon, cashCoupon, cashCoupon, cashCoupon + face)
ts         <- c(1,2,3,4)

ytm        <- (IRR(cf0 = -___, cf = ___, times = ___)) * 100 * 2
ytm
```


## Session Info

```{r}
devtools::session_info()
```

```{r}
date()
sessionInfo()
```

```{r}
date()
Sys.getenv()
```


