---
title:  "Exercise 10-A: SEC Edgar Exercise"
author: "Larry Tentor"
date:   "`r (Sys.Date())`"
output:
  html_document:
    df_print: kable
    theme: simplex
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: no
    urlcolor: blue
  pdf_document:
    toc: yes
---

```{r setupExclude, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r setup, include=FALSE}
# List selected libraries
library(tidyverse)
library(edgar)
library(XBRL)
# Setting stringsAsFactors = FALSE is recommended to avoid data frames creating factors from character vectors.
options(stringsAsFactors = FALSE)
```

# Focus

The focus of this exercise is accessing the data on the SEC EDGAR system.

# CIK Reference

Look up the follow CIK codes on SEC Website

| CIK        | Entity              |
|------------|---------------------|
| 0001652044 | Alphabet, Inc.      |
|            | Apple, Inc.         |
|            | Amazon Com Inc      |
| 0000789019 | Microsoft Corp      |


A company's CIK can be located on the [SEC website](https://www.edgarcompany.sec.gov/servlet/CompanyDBSearch?page=main)

# Entity Filings

Download the 2018, 2019 and 2020 reports on file for the above entites

## getFilingInfo

This looks at the list of filings of a corporate entity.

```{r FilingList, echo=TRUE, results=FALSE}

```

Filter the filings for Annual Reports (10-K) and sort the filings by date.

```{r}

```

## getFilings

Now lets download Apple's filings to a local directory.

```{r FilingsDownload, echo=TRUE, results=FALSE}
```

```{r}
```

Where are the downloaded files?

