---
title: "Exercise 02-C"
author: "(fill in your name)"
output:
  html_document:
    df_print: kable
    theme: simplex
    toc: true
    urlcolor: blue
    toc_float:
      collapsed: false
      smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#install.packages(tvm)
library(tvm)
```

## Exercise Directions

This file contains an exercise.  Please read the text and adjust the necessary code chunks (between \`\`\` symbols), to accomplish the stated goal.

## Time Value of Money

### Load Federal Funds Rate

As a bank employee you are responsible for your reserves with the Federal Reserve System.

You need to monitor the Federal Funds rate and calculate the earnings from excess Reserves or the costs of borrowing others reserves.

Determine the file name for the Federal Funds within the data directory.

```{r FederalFunds}
my_file <- "../data/___"

fedfund <- read.csv(___,___,___)

tail(fedfund)
```


### November 2019 Reserves

If our bank had 10,000,000 USD in excess reserves for one day in November 2019 how much interest would it earn at the federal funds rate.

```{r Interest}

cash      <- ___
obs       <- subset(fedfund,DATE==___)
r         <- ___

interest  <- ___

print(interest)

```


## Session Info

```{r}
devtools::session_info()
```

```{r}
date()
sessionInfo()
```

```{r}
date()
Sys.getenv()
```


