---
title: "Exercise 01-A"
author: "(fill in your name)"
output:
  html_document:
    df_print: kable
    theme: simplex
    toc: true
    urlcolor: blue
    toc_float:
      collapsed: false
      smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Exercise Directions

This file contains an exercise.  Please read the text and adjust the necessary code chunks (between ``` symbols), to accomplish the stated goal.

## Time Value of Money

### Exercise Problem

You firm has expected cash flows from a contract of \$1,000, \$2,000 and \$3,000. 


```{r}

cf       <- c(___,___,___)  # This is a vector c()ombine!
r        <- 2.5/100
g        <- 1+r
year     <- 1:length(cf)
discount <- 1/g^year
pvN      <- cf * discount 
pv       <- sum(pvN)

#print(discount)
#print(pvN)
print(pv)
```

### Subtraction

Update the variables to calculate one thousand two hundred and seven minus forty seven.

```{r Subtration}
# Subtraction
4781 - 832
```

### Multiplication

Let's calculate three times seventy four.

```{r Multiplication}
# Multiplication
333 * 7
```

### Division $\div$

Determine one quarter of two hundred and four.

```{r Division}
# Division
333 / 3
```





## Session Info

```{r}
devtools::session_info()
```

```{r}
date()
sessionInfo()
```

```{r}
date()
Sys.getenv()
```


