---
title: "Exercise 02-A"
author: "(fill in your name)"
output:
  html_document:
    df_print: kable
    theme: simplex
    toc: true
    urlcolor: blue
    toc_float:
      collapsed: false
      smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Exercise Directions

This file contains an exercise.  Please read the text and adjust the necessary code chunks (between \`\`\` symbols), to accomplish the stated goal.

## Time Value of Money

### TVM Problem 1

You firm has expected cash flows from a contract of \$1,000, \$2,000 and \$3,000. The prevaling interest rate is 5% per annum.  Calculate the present value.  Update the ___ sections to provide the correct answer.


```{r TVM01}
cf       <- ___
r        <- ___
g        <- 1+r
year     <- 1:length(cf)    
discount <- 1/g^year
pvN      <- cf * discount # What is stored in this variable?
pv       <- sum(pvN)

print(pv)
```

### TVM Problem 2

You just got an update and additional detail on the term structure of interest rates.  The rate for period 1($_0r_1$) is 5%, the rate for period 2 ($_0r_2$) is 6%, and the rate for period 3 ($_0r_3$) is 7%.  What changes do you propose below?  Update the ___ sections to provide the correct answer.


```{r}

cf       <- ___ 
r        <- ___
g        <- 1+r
year     <- 1:length(cf)    
discount <- 1/g^year
pvN      <- cf * discount 
pv       <- sum(pvN)

#print(discount)
#print(pvN)
print(pv)
```


## Session Info

```{r}
devtools::session_info()
```

```{r}
date()
Sys.getenv()
```


