---
title: "Money Market Calculations (Exercise 04-A) Solution"
author: "(fill in your name)"
output:
  html_document:
    df_print: kable
    theme: simplex
    toc: true
    urlcolor: blue
    toc_float:
      collapsed: false
      smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#install.packages(tvm)
library(tidyverse)
```

# Exercise Directions

This file contains an exercise.  Please read the text and adjust the necessary code chunks (between \`\`\` symbols), to accomplish the stated goal.    The entire exercise will not knit since sections of the code have been filled with `___` where you need to complete the code.  Use the run above and run button on each chunk for intermediate results.

# Money Markets

## 1. Problem (Saunders and Cornett, Adjusted from slides)

A \$5M investment in 180 day commercial paper has a 1.5% discount yield. An equivalent size and risk 180 day CD has a 1.5% single payment yield.  Which security offers the better return?   

### Commercial Paper

Calculate the initial price of the commercial paper and find the bond equivalent yield.

```{r CommercialPaper}
# from i_d formula
id_cp <- 0.015
Pf_cp <- 5000000
n     <- 180
P0_cp <- -(id_cp * n / 360 * Pf_cp) + Pf_cp

P0_cp

ibe_cp <- (Pf_cp - P0_cp)/P0_cp * 365 / n

ibe_cp

```
### CD Calculations

convert the given single payment yield into a bond equivalent.

```{r CD}
isp_cd <- 0.015 
ibe_cd <- isp_cd * 365 / 360

ibe_cd

```

### Comparison

Compare the bond equivalent yield for the commercial paper and the certificate of deposit.

```{r Compare}
if (ibe_cp > ibe_cd) {
  print('Commercial Paper has better yield')
} else {
  print('CD has better yield')
}

```

## 7. Problem (Page 167, Saunders and Cornett)

You can purchase a T-bill that is 95 days from maturity for \$9,965. The T-bill has a face value of $10,000. (LG 5-2)

a. Calculate the T-bill’s quoted yield.
b. Calculate the T-bill’s bond equivalent yield.
c. Calculate the T-bill’s EAR.


### a. Calculate Quoted Yield.

Fill in the below variables and provide the function for $i_d$.

```{r DiscountYield02}
Pf <- 10000
P0 <- 9965
n  <- 95
id <- (Pf-P0)/Pf*360/n

print(id*100)
```

### b. Calculate Bond Equivalent Yield.

Provide the formula for bond equivalent yield $i_{be}$.

```{r bondEquivalentYield02}
ibe <- (Pf-P0)/P0*365/n

print(ibe*100)
```

### c. Calculate Effective Annual Return


```{r ear02}

ear <- ((1+(ibe/(365/n)))^(365/n))-1
  
print(ear)
```


## 10. Problem (Page 167, Saunders and Cornett)

A T-bill that is 225 days from maturity is selling for \$98,850. The T-bill has a face value of \$100,000. (LG 5-2)

a. Calculate the discount yield
b. Calculate the bond equivalent yield
c. Calculate the EAR

Calculate the discount yield, bond equivalent yield, and EAR on the T-bill if it matures in 300 days.

### a. Calculate the discount yield

Provide all necessary for the discount yield calculation and print the resulting answer.

```{r discountYield03A}
Pf <- 100000
P0 <- 98850
n  <- 225
id <- (Pf-P0)/Pf*360/n

print(id*100)

```


### b. Calculate the bond equivalent yield

Provide all necessary for the bond equivalent yield calculation and print the resulting answer.

```{r bondEquivalentYield03B}
ibe <- (Pf-P0)/P0*365/n

print(ibe*100)
```

### c. Calculate the EAR

Provide all necessary for the effective annual return calculation and print the resulting answer.


```{r EAR03C}
ear <- ((1+(ibe/(365/n)))^(365/n))-1
  
print(ear)

```

## Session Info

```{r}
devtools::session_info()
```

```{r}
date()
sessionInfo()
```

```{r}
date()
Sys.getenv()
```


