---
title: "Treasury Auction Data (Exercise 04-B)"
author: "(fill in your name)"
output:
  html_document:
    df_print: kable
    theme: simplex
    toc: true
    urlcolor: blue
    toc_float:
      collapsed: false
      smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#install.packages(tvm)
library(tidyverse)
library(xml2)
```

# Exercise Directions

This file contains an exercise.  Please read the text and adjust the necessary code chunks (between \`\`\` symbols), to accomplish the stated goal.  The entire exercise will not knit since sections of the code have been filled with `___` where you need to complete the code.  Use the run above and run button on each chunk for intermediate results.

# Treasury Auction Data

## Import Treasury Auction Data

The treasury action results are available in data sets on the release page, 
[Treasury Auction Data](https://www.treasurydirect.gov/instit/annceresult/press/press_auctionresults.htm).

Please open the T-bill 4-week section and select the 01/28/2020 pdf for competitive results.  Review this [pdf](https://www.treasurydirect.gov/instit/annceresult/press/preanre/2020/R_20200130_2.pdf) file.

Let's first review the treasury auction data available.

```{r ImportAuctionData}


auctionXml    <- read_xml('https://www.treasurydirect.gov/xml/R_20200130_2.xml')  # New function, special format file
auctionList   <- as_list(auctionXml)                                              # Convert to an R list
class(auctionXml)
class(auctionList)
```

## Explore Auction Data

This section explores what was read into R.  XML is a format that allows extensive data storage, it can be a tad complex to explore what is available.  We have used `read_xml` and `as_list` to place the file data directly in a list structure.  This list structure itself contains other lists.  In the next block we extract `auctionAnnouncement` and `auctionResults`

```{r ExploreAuctionData}
length(auctionList)

length(auctionList$AuctionData)
length(auctionList$AuctionData$AuctionAnnouncement)
length(auctionList$AuctionData$AuctionResults)
```

```{r ExploreAuctionData2}
auctionAnnouncement <- auctionList$AuctionData$AuctionAnnouncement
auctionResults      <- auctionList$AuctionData$AuctionResults

length(auctionAnnouncement)
length(auctionResults)
```


## Auction Announcement

Does this data compare to the [Auction Annoucement pdf](https://www.treasurydirect.gov/instit/annceresult/press/preanre/2020/A_20200128_2.pdf) file released on this date?

<< Your Comment Here >>

```{r ExploreAuctionAnnouncement}
auctionAnnouncement
```
## Auction Results

Does this data compare to the [Auction Results pdf](https://www.treasurydirect.gov/instit/annceresult/press/preanre/2020/R_20200130_2.pdf) file released on this date?

<< Your Comment Here >>


```{r ExploreAuctionResults}
auctionResults
```

## Calculate the coverage ratio 

The total tendered is extracted and converted to a number for you.  You will need to complete extracting total accepted and calculating the coverage ratio.

Does this coverage ratio match that computed by the treasury?

<< Your Comment Here >>

```{r ColumnNames}
totalTendered <- as.numeric(auctionResults$___)
class(totalTendered)
totalAccepted <- as.numeric(auctionResults$___)
class(totalAccepted)
coverageRatio <- ___/___

format(totalTendered, scientific=FALSE)
format(totalAccepted, scientific=FALSE)
coverageRatio

```


## Auction Summary

How much money did the treasury borrow in this 4-week auction and how much interest will be paid?  Calculate this below and display.

```{r Summary}
faceValue    <- ___
borrowed     <- ___ * as.numeric(auctionResults$HighPrice[[1]])/100
interestRate <- as.numeric(auctionResults$HighDiscountRate[[1]])
interestPaid <- ___ - borrowed

  
print(paste0('The Treasury borrowed $', format(borrowed, big.mark=",", scientific = FALSE), ' at an interest payment of $', format(interestPaid, big.mark=",", scientific = FALSE),' resulting in face value of $', format(faceValue, big.mark=",", scientific = FALSE)))  
```


## Session Info

```{r}
devtools::session_info()
```

```{r}
date()
sessionInfo()
```

```{r}
date()
Sys.getenv()
```


