---
title:  "Mortgage Markets"
author: "Larry Tentor"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: "presentation.css"
    nature:
      highlightLines: true
      highlightStyle: solarized-dark
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
#output: ioslides_presentation
library(FinancialMath)
library(YieldCurve)
knitr::opts_chunk$set(echo = FALSE)
```

class: center, middle

# Attribution

McGraw Hill has provided power point slides that were substantially used to construct this R Markdown deck.

---

# Quiz Items

---

## Price Volatility

A 10-year maturity zero coupon bond will have lower price volatility than a 10-year bond with a 10 percent coupon.

- True
- False

--

Answer- False

What is the princple behind this?

---

## T-bill Auction

In the T-bill auction process, the competitive bidder is guaranteed a \_\_\_\_\_\_\_\_\_\_\_ and a noncompetitive bidder is guaranteed a \_\_\_\_\_\_\_\_\_\_\_.

- minimum price; maximum price.
- maximum price; minimum price.
- maximum price; given quantity.
- minimum price; maximum quantity.
- None of these choices are correct.

--

Answer- maximum price; given quantity

---

# Class Problems

---

## Problem A: House Purchase

You plan to purchase a $130,000 house using a 30-year mortgage obtained from your local credit union.  The mortgage rate offered is 4.125%. You plan to make a 20% down payment. 

---

## Problem A: House Purchase

You plan to purchase a $130,000 house using a 30-year mortgage obtained from your local credit union.  The mortgage rate offered is 4.125%. You plan to make a 20% down payment. 


```{r A, echo=TRUE}
purchase    <- 130000
term        <- 30                   # Annual term
termM       <- term*12              # Monthly term
rate        <- 0.04125              # Annual rate
rateM       <- rate/12              # Monthly rate
downpayment <- 0.20 * purchase
principle   <- purchase - downpayment
pmt         <- principle/((1- (1/((1+rateM)^(termM)))) /rateM)
c(principle, pmt)

```

---

## Problem B: House Refinace

Five years ago you purchased a $360,000 house.  You paid 20% down to avoid PMI fees.  At this time, you paid 5% on a 30-year mortgage.

You believe that it may be a good time to refinance with current rates running at 4% for a 30 year mortgage.  It will cost around $2500 in fees to refinance.  How many months would it take to recoup these fees? 

--

What steps are necessary?

--

a. Principle remaining on first loan?
$principle_n = (1-\frac{1}{(1+r)^{term*12-n}})/r/((1-(1+r)^{term*12})/r)*principle_0$

---

## Problem B: House Refinace- Step 1

Five years ago you purchased a $360,000 house.  You paid 20% down to avoid PMI fees.  At this time, you paid 5% on a 30-year mortgage.

You believe that it may be a good time to refinance with current rates running at 4% for a 30 year mortgage.  It will cost around $2500 in fees to refinance.  How many months would it take to recoup these fees? 


```{r B-1, echo=TRUE}
purchase    <- 360000
term        <- 30                   # Annual term
termM       <- term*12              # Monthly term
rate        <- 0.05                 # Annual rate
rateM       <- rate/12              # Monthly rate
downpayment <- 0.20 * purchase
principle   <- purchase - downpayment
pmt         <- principle/((1- (1/((1+rateM)^(termM)))) /rateM)
principle_60 <- ((1 - (1/((1+rateM)^(termM-60))))/rateM) /
                ((1 - (1/((1+rateM)^(termM   ))))/rateM) * principle
c(principle, pmt, principle_60)

```

---

## Problem B: House Refinace- Step 2

Five years ago you purchased a $360,000 house.  You paid 20% down to avoid PMI fees.  At this time, you paid 5% on a 30-year mortgage.

You believe that it may be a good time to refinance with current rates running at 4% for a 30 year mortgage.  It will cost around $2500 in fees to refinance.  How many months would it take to recoup these fees? 

```{r B-2, echo=TRUE}
term2       <- 30                   # Annual term
<<<<<<< HEAD
term2M      <- term2*12             # Monthly term
rate2       <- 0.04                 # Annual rate
rate2M      <- rate/12              # Monthly rate
pmt2        <- principle_60/((1- (1/((1+rate2M)^(term2M)))) /rate2M)
=======
term2M      <- term*12              # Monthly term
rate2       <- 0.04                 # Annual rate
rate2M      <- rate/12              # Monthly rate
pmt2         <- principle_60/((1- (1/((1+rate2M)^(term2M)))) /rate2M)
>>>>>>> 5e171c4603c962687d680a0c481fd94911bf16af
savingM    <- pmt - pmt2
nBreakeven  <- ceiling(2500/savingM)

c(pmt, pmt2, savingM, nBreakeven)

```

---

## Mortgage Closing Statement

Let's walk through a mortgage closing statement as a valuable consumer finance lesson!

https://www.consumerfinance.gov/owning-a-home/closing-disclosure/
