---
title: "BAML Data Research"
author: "Larry Tentor"
date: "`r (Sys.Date())`"
output:
  html_document:
    df_print: kable
    theme: simplex
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: no
    urlcolor: blue
  pdf_document:
    toc: yes
---

```{r setupExclude, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r setup, include=TRUE}
# List selected libraries
suppressWarnings(library(tidyverse))
suppressWarnings(library(fredr))
```

# Federal Reserve Bank API

You must complete the following steps
  1. Register for a Federal Reserve Bank API key
  2. Create a text file on your local machine. (In windows Explorer > right click > New > Create Document)
  3. Save the file with the name "FRED.key"
  4. Place the key on the first line of the text file and save
  5. Transfer file to lesson05 directory.

```{r}
# Read Federal Reserve Economic Database (FRED) user key
#
# This will need to be configured for each user 
# by signing up for an account at
# https://research.stlouisfed.org/useraccount/apikeys
#
# Then place the api key on the first line of the file FRED.key in the lesson directory.
#
# This key is a long hex number that looks like
#
# ffff231e4928f1f49bb4a3699834d3ca
#
fredFile          <- read.csv('../FRED.key', header = FALSE, sep = ",", dec = ".", stringsAsFactors = FALSE)
GetYourOwnFredKey <- fredFile$V1[1]
fredr_set_key(GetYourOwnFredKey)
```

# BAML Data

## Load BAML data

```{r}
fileData <- '../data/ml5cmz10.csv'

BamlColClasses <- 
  c( "character", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric") 

BAML            <- read.csv( fileData, header = TRUE, skip = 1, sep = ","
                           , dec = ".", colClasses = BamlColClasses 
                           , stringsAsFactors = FALSE)
BAML$DateString <- BAML$Date
BAML$Date       <- as.Date(BAML$DateString,'%m/%d/%Y')

head(BAML)

```

# FRED Data

## 10 Year Constant Maturity Rate

```{r}
Rate10year      <- fredr(series_id = "DGS10")
Rate10year$name <- "Ten Year"
head(Rate10year)
```



```{r}
ggplot(Rate10year, aes(date, value)) + 
  geom_line() + 
  xlab("Date") + 
  ylab("Rate [%]") + 
  ggtitle("History of Ten Year Constant Maturity Rate")
```

## BAML Index: ICE BofAML US High Yield Master II Option-Adjusted Spread


```{r}
H0A0      <- fredr(series_id = "BAMLH0A0HYM2")
H0A0$name <- "H0A0"
head(H0A0)

C0A4      <-  fredr(series_id = "BAMLC0A4CBBB")
C0A4$name <- "C0A4"

```

```{r}
ggplot(H0A0, aes(date, value)) + 
  geom_line() + 
  xlab("Date") + 
  ylab("Rate [%]") + 
  ggtitle("History of High Yield Master II OAS")
```



# Assembly data


```{r}
#Stacked
dataStack    <- rbind(Rate10year,H0A0)

# Wide
dataWide     <- BAML %>% left_join(Rate10year[c("date","value")],by = c("Date" = "date"))
colnames(dataWide)[9] <- "Rate10Year" 
dataWide     <- dataWide %>% left_join(H0A0[c("date","value")],by = c("Date" = "date"))
colnames(dataWide)[10] <- "H0A0_OAS" 
dataWide     <- dataWide %>% left_join(C0A4[c("date","value")],by = c("Date" = "date"))
colnames(dataWide)[11] <- "C0A4_OAS" 

head(dataWide)

```

## Check if same as FRED

Surprising some of the values are different by a basis point or two.  Yet the majority of them line up directly. See graph.

```{r}

check <- dataWide[c("Date","H0A0","H0A0_OAS")]
check$compare <- check$H0A0 - check$H0A0_OAS*100
sum(abs(check$compare))
head(check)

ggplot() + 
  geom_line(data = dataWide, aes(x = Date, y = H0A0), color = "blue") +
  geom_line(data = dataWide, aes(x = Date, y = H0A0_OAS*100), color = "red") +
  xlab('Dates') +
  ylab('Rate') +
  scale_shape_discrete(name  ="DiscountRate",
                          labels=c("fedfund", "indianDiscount"))


```

## Conclusion

BAML did not provide anything that was not in the public domain, and does not even have a well specified project.

