---
title: "Assignment 02-A"
author: "(fill in your name)"
output:
  html_document:
    df_print: kable
    theme: simplex
    toc: true
    urlcolor: blue
    toc_float:
      collapsed: false
      smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```

## Assignment Directions

This file contains an assignment.  Please read the text and adjust the necessary code chunks (between \`\`\` symbols), to accomplish the stated goal.  This assignment is to be completed by each student, no digital sharing is allowed.  Concepts may be discussed, yet submission much be completed by submitting student.

## Specify file

In this assignment you will first load the Federal Funds rates.  Locate the Federal Funds data file within lesson 02.

```{r fileLocation}
my_file <- "../data/___.csv"
```

## Load Federal Funds

This will require reading a csv file.  We have done this using the function 'read.csv'.  Do make certain that the date column is stored in a date format not a character string or factor.  We have done two examples of how to properly use Date column.  

```{r}
fedfund <- read.csv(___, header = ___, colClasses = c(___,___))
```

## Examine the content of the data.frame

Replace "function_name" with the correct name of the function to examine the last entiries in the data frame.

```{r}
#function_name(variable_name)
tail(___)
```

## Data Manipulation

Make certain the date column in the data frame is a date type.  if you are uncertain type '?as.Date'

```{r}
if (class(fedfund$DATE) == "Date") {
  print('Already date datatype')
} else {
  fedfund$DATE <- as.Date(___)
  print('Adjusted datatype to date')  
}

```

## Load Indian Discount Rate

This will require reading a a second csv file (INTDSRINM193N).  Do make certain that the date column is stored in a date format not a character string or factor.  We have done two examples of how to properly use Date column.  But this date is in a different format, so requires a different solution.

International Monetary Fund, Interest Rates, Discount Rate for India [INTDSRINM193N], retrieved from FRED, Federal Reserve Bank of St. Louis; https://fred.stlouisfed.org/series/INTDSRINM193N, January 20, 2020.

```{r}
my_file        <- "../data/___.csv"
indianDiscount <- read.csv(___, header = ___, colClasses = c(___,___))
indianDiscount$DATE <- as.Date(indianDiscount$DATE,format="___")
tail(indianDiscount)
```

## Plot the two counties Discount Rates

```{r}

ggplot() + 
  geom_line(data = fedfund, aes(x = DATE, y = FEDFUNDS), color = "blue") +
  geom_line(data = indianDiscount, aes(x = DATE, y = INTDSRINM193N), color = "red") +
  xlab('Dates') +
  ylab('Discount Rate') +
  scale_shape_discrete(name  ="DiscountRate",
                          labels=c("fedfund", "indianDiscount"))


```

## Contrast the two counties Discount Rates

What do you see in this graph, does it look as you expect, what questions does it raise?

Include a comment on the the discount rate over time for both countries.

INSERT ANSWER PARAGRAPH HERE

## Submission

Submit the single html file "homework02-A.html", Blackboard may require that you zip it prior to submission.  Leave the session info that follows for debugging purposes for the instructor.


## Session Info

```{r}
devtools::session_info()
```

```{r}
date()
sessionInfo()
```

```{r}
date()
Sys.getenv()
```


