
---
title: "Cuts Minimal Working Example (MWE)"
author: "Larry Tentor"
date: "`r (Sys.Date())`"
output:
  html_document:
    df_print: kable
    theme: simplex
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: no
    urlcolor: blue
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Motivation

We have a range of values and we wish to assign a text string based on a specified range of values.

## Data

```{r DataSample}
## 
dataSample <- read.csv(text= "
Name,Score,C
Larry,3,4
Bert,7,9
William,5,4
Sri,5,6
Meredith,6,6
Evan,8,12",stringsAsFactor=FALSE)

```


## Two Bucket Array Example

This section uses the `ifelse` function, whcih evaluates a relationship and sets a value in the TRUE case and the FALSE case.

```{r TwoBucketArray}

dataSample$Bucket2Array <- ifelse(dataSample$Score>5,"High","Low")

dataSample

```

## Three Bucket Array Example

This section uses multiple levels of `ifelse` to create three buckets.  If additional buckets are necessary continue nesting `ifelse`.
```{r ThreeBucketArray}

dataSample$Bucket3Array <- ifelse(dataSample$Score>5,ifelse(dataSample$Score>7,"Ultra","High"),"Low")

dataSample

```

## The Cuts Function

The cuts function offers a more robust implmentation to divide a numeric dataset into different regions.  

```{r cuts}

## This determine regions within the cut algorithm, based on the three desired cuts
dataSample$BucketCut <- cut(dataSample$Score,breaks=3,labels=c("Low","Medium","High"))

## Here we specify the breaks
# You will want to check if the value on the edge is assigned to the higher category or the lower category.
dataSample$Bucket2Cut <- cut(dataSample$Score,breaks=c(0,4,6,8),labels=c("Low","Medium","High"))

dataSample

```


# Appendix

R, like Excel, has many ways to accomplish different tasks.  Here are others, we have not had extensive conversations on looping in class.

## Two Bucket Looping Example

```{r TwoBucketLoop}
for (i in (1:nrow(dataSample)))
{
dataSample$Bucket2Loop[i] <- ifelse(dataSample[i,2]>5,"High","Low")
}

dataSample

```

## Three Bucket Looping Example

```{r ThreeBucketLoop}
for (i in (1:nrow(dataSample)))
{
dataSample$Bucket3Loop[i] <- ifelse(dataSample[i,2]>5,ifelse(dataSample[i,2]>7,"Ultra","High"),"Low")
}

dataSample

```
