---
title: "Exercise 05-A: Federal Reserve Mortgage Market Data (solution)"
author: "Larry Tentor"
date: "`r (Sys.Date())`"
output:
  html_document:
    df_print: kable
    theme: simplex
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: no
    urlcolor: blue
  pdf_document:
    toc: yes
---

```{r setupExclude, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r setup, include=TRUE}
# List selected libraries
suppressWarnings(library(tidyverse))
suppressWarnings(library(fredr))
```

# Federal Reserve Bank API

You must complete the following steps
  1. Register for a Federal Reserve Bank API key
  2. Create a text file on your local machine. (In windows Explorer > right click > New > Create Document)
  3. Save the file with the name "FRED.key"
  4. Place the key on the first line of the text file and save
  5. Transfer file to lesson05 directory.

```{r}
# Read Federal Reserve Economic Database (FRED) user key
#
# This will need to be configured for each user 
# by signing up for an account at
# https://research.stlouisfed.org/useraccount/apikeys
#
# Then place the api key on the first line of the file FRED.key in the lesson directory.
#
# This key is a long hex number that looks like
#
# ffff231e4928f1f49bb4a3699834d3ca
#
fredFile          <- read.csv('../FRED.key', header = FALSE, sep = ",", dec = ".", stringsAsFactors = FALSE)
GetYourOwnFredKey <- fredFile$V1[1]
fredr_set_key(GetYourOwnFredKey)
```

# Mortgage Debt

### Residential Debt

Instructions
  1. Replace the series_id with the residential mortgages id (see below for suggested citation)
  2. Select a label name and replace ___
  
  Suggested Citation:
Board of Governors of the Federal Reserve System (US), Mortgage Debt Outstanding by Type of Property: One- to Four-Family Residences [MDOTP1T4FR], retrieved from FRED, Federal Reserve Bank of St. Louis; https://fred.stlouisfed.org/series/MDOTP1T4FR, February 8, 2020.  

```{r mortgageDebtResidential}
mortgageDebtResidential      <- fredr(series_id = "MDOTP1T4FR")
mortgageDebtResidential$name <- "Residential"
head(mortgageDebtResidential)
```



```{r mortgageDebtResidentialPlot}

ggplot(mortgageDebtResidential, aes(date, value)) + 
  geom_line() + 
  xlab("Date") + 
  ylab("Mortgage Debt [million $]") + 
  ggtitle("History of Mortgage Debt")

```



### Farm Debt

Instructions
  1. Replace the series_id with the residential mortgages id (see below for suggested citation)
  2. Select a label name and replace ___
  
  Suggested Citation:
Board of Governors of the Federal Reserve System (US), Mortgage Debt Outstanding by Type of Property: Farm [MDOTPFP], retrieved from FRED, Federal Reserve Bank of St. Louis; https://fred.stlouisfed.org/series/MDOTPFP, February 13, 2020.
  
```{r mortgageDebtFarm}
mortgageDebtFarm      <- fredr(series_id = "MDOTPFP")
mortgageDebtFarm$name <- "Farm"
tail(mortgageDebtFarm)
```
```{r mortgageDebtFarmPlot}

ggplot(mortgageDebtFarm, aes(date, value)) + 
  geom_line() + 
  xlab("Date") + 
  ylab("Mortgage Debt [million $]") + 
  ggtitle("History of Mortgage Debt")

```

### MultiFamily Debt


Instructions
  1. Replace the series_id with the multi-family mortgages id (see below for suggested citation)
  2. Select a label name and replace ___
  
Suggested Citation:
Board of Governors of the Federal Reserve System (US), Mortgage Debt Outstanding by Type of Property: Multifamily Residences [MDOTPMFR], retrieved from FRED, Federal Reserve Bank of St. Louis; https://fred.stlouisfed.org/series/MDOTPMFR, February 13, 2020.


```{r mortgageMultiFamily}
mortgageDebtMultiFamily      <- fredr(series_id = "MDOTPMFR")
mortgageDebtMultiFamily$name <- "Multi-Family"
tail(mortgageDebtMultiFamily)
```


```{r mortgageMultiFamilyPlot}

ggplot(mortgageDebtMultiFamily, aes(date, value)) + 
  geom_line() + 
  xlab("Date") + 
  ylab("Mortgage Debt [million $]") + 
  ggtitle("History of Mortgage Debt")

```

### Commericial Debt


Instructions
  1. Replace the series_id with the commericial mortgages id (see below for suggested citation)
  2. Select a label name and replace ___
  
Suggested Citation:
Board of Governors of the Federal Reserve System (US), Mortgage Debt Outstanding by Type of Property: Nonfarm and Nonresidential [MDOTPNNRP], retrieved from FRED, Federal Reserve Bank of St. Louis; https://fred.stlouisfed.org/series/MDOTPNNRP, February 13, 2020.


```{r mortgageCommerical}
mortgageDebtCommercial      <- fredr(series_id = "MDOTPNNRP")
mortgageDebtCommercial$name <- "Commercial"
head(mortgageDebtCommercial)
```


```{r mortgageCommercialPlot}

ggplot(mortgageDebtCommercial, aes(date, value)) + 
  geom_line() + 
  xlab("Date") + 
  ylab("Mortgage Debt [million $]") + 
  ggtitle("History of Mortgage Debt")

```


### Assembly data: Stack

- Can you think of a time you have stacked data

```{r}
#Stacked
mortgageStack    <- rbind(mortgageDebtResidential,mortgageDebtFarm, mortgageDebtMultiFamily, mortgageDebtCommercial)
head(mortgageStack %>% filter(date == '1995-10-01'))
```
### Graph 1995 & 2016

```{r}

mortgage19952016 <- mortgageStack %>% filter(date=='1995-10-01' | date=='2016-10-01')
mortgage19952016

```

Bar Plot

```{r}

barPlot   <- ggplot(mortgage19952016, aes(x="", y=value, fill=name))+
               geom_bar(width = 1, stat = "identity") +
               facet_wrap( ~ date )
barPlot

```
Pie Chart

```{r}

pieChart  <- ggplot(mortgage19952016, aes(x="", y=value, fill=name))+
               geom_bar(width = 1, stat = "identity") +
               coord_polar("y", start=0) +
               facet_wrap( ~ date )
               
pieChart

```


