---
title: "TVM and Federal Reserve in R"
author: "Larry Tentor"
always_allow_html: true
output:
  ioslides_presentation
---

```{r setupExclude, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(tidyverse)
library(tvm)
library(FinancialMath)
```


## Interest Rates

$PV = \frac{CF_1}{(1+r)^1} + \frac{CF_2}{(1+r)^2} + ... + \frac{CF_n}{(1+r)^n}$

$CF_t$ = cash flow in period t (t = 1, …, n)

n = number of periods in the investment horizon

Problem: We are owed \$2,000 at the end of the first year and \$4,000 at the end of the second year.  The nominal interest rate is 2.5% per annum. What is the present value?


## Present Value - Problem Specific

```{r PV_ProblemSpecific}
pv <- 2000/(1+2.5/100) + 4000/(1+2.5/100)^2
pv
```

## Present Value - With Variables

```{r PV_withVariables}
cf1 <- 2000
cf2 <- 4000
r   <- 2.5/100
pv  <- cf1/(1+r)+cf2/(1+r)^2
pv
```

## Present Value - With vectors

```{r PV_withVectors}
cf       <- c(2000,4000)  # This is a vector c()ombine!
r        <- 2.5/100
g        <- 1+r
year     <- 1:length(cf)  # What does this create?
discount <- 1/g^year
pvN      <- cf * discount 
pv       <- sum(pvN)

#print(discount)
#print(pvN)
print(pv)
```

## Extended Problem

We now found out the the cash flow stream included a payment at the end of year three of \$3,000 and end of year four of \$2,000.

Which of the three above solutions requires the fewest changes and scales most easily.

## Extended Problem with Vectors

```{r PV_ExtendedwithVectors}
cf       <- c(2000,4000,3000,2000)  # This is a vector c()ombine!
r        <- 2.5/100
g        <- 1+r
year     <- 1:length(cf)
discount <- 1/g^year
pvN      <- cf * discount 
pv       <- sum(pvN)

#discount
#pvN
pv
```
What did we have to do to get this to work?

## Exercise 02-A.

## Library Functions

R has the ability to extend it capabilities by others efforts.  This is most common done in sharing a package.  This is a collection of functions that you may leverage for your own calculations.

One such package is 'tvm' (Time Value of Money) which we can use for our calculations.

For the Excel user, the following functions will be known

* npv
* xnpv
* irr
* xirr
* pmt
* rate

## Net Present Value (NPV) 01

Find the Net Present Value of 

```{r TVM01, echo = FALSE}
library(tvm)
cf <- c(2000,4000)
t  <- c(1,2)
r  <- 0.025
cf.analysis(cf=cf,times=t,i=r,time.d =TRUE)
```

## Net Present Value (NPV) 02 

```{r TVM02}
library(tvm)
cf <- c(2000,4000)
t  <- c(1,2)
r  <- 0.025

npv(i = r, cf = cf, ts = t)
```
## Discount Value: Term Structure and Rate Curves

```{r TVM03}
library(tvm)

cf        <- c(2000,4000)     # This is a vector c()ombine!
r         <- c(0.025,0.025)
rateCurve <- rate_curve(rates = r, rate_type = "zero_eff")
pv        <- disc_value(rateCurve, cf = cf)

print(pv)

```


## Exercise 02-B.


## Session Info

```{r}
devtools::session_info()
```

```{r}
date()
sessionInfo()
```



