---
title: "Present Value and Federal Reserve in R"
author: "Larry Tentor"
always_allow_html: true
output:
  ioslides_presentation
---

```{r setupExclude, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(tidyverse)
```


## Interest Rates

$PV = \frac{CF_1}{(1+r)^1} + \frac{CF_2}{(1+r)^2} + ... + \frac{CF_n}{(1+r)^n}$

$CF_t$ = cash flow in period t (t = 1, …, n)

n = number of periods in the investment horizon

Problem: We are owed \$2,000 at the end of the first year and \$4,000 at the end of the second year.  The nominal interest rate is 2.5% per annum. What is the present value?


## Present Value - Problem Specific

```{r PV_ProblemSpecific}
pv <- 2000/(1+2.5/100) + 4000/(1+2.5/100)^2
pv
```

## Present Value - With Variables

```{r PV_withVariables}
cf1 <- 2000
cf2 <- 4000
r   <- 2.5/100
pv  <- cf1/(1+r)+cf2/(1+r)^2
pv
```

## Present Value - With vectors

```{r PV_withVectors}
cf       <- c(2000,4000)  # This is a vector c()ombine!
r        <- 2.5/100
g        <- 1+r
year     <- 1:length(cf)  # What does this create?
discount <- 1/g^year
pvN      <- cf * discount 
pv       <- sum(pvN)

#print(discount)
#print(pvN)
print(pv)
```

## Extended Problem

We now found out the the cash flow stream included a payment at the end of year three of \$3,000 and end of year four of \$2,000.

Which of the three above solutions requires the fewest changes and scales most easily.

## Extended Problem with Vectors

```{r PV_ExtendedwithVectors}
cf       <- c(2000,4000,3000,2000)  # This is a vector c()ombine!
r        <- 2.5/100
g        <- 1+r
year     <- 1:length(cf)
discount <- 1/g^year
pvN      <- cf * discount 
pv       <- sum(pvN)

#discount
#pvN
pv
```
What did we have to do to get this to work?

## Exercise 02-A.


## Session Info

```{r}
devtools::session_info()
```

```{r}
date()
sessionInfo()
```



