---
title: "Treasury Auction (Activity 04)"
author: "(fill in your name)"
output:
  html_document:
    df_print: kable
    theme: simplex
    toc: true
    urlcolor: blue
    toc_float:
      collapsed: false
      smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#install.packages(tvm)
library(tidyverse)
```

# Activity Directions

This file contains the bids of a treasury auction.  It is your job to determine the high rate and allocate the awards.

# Treasury Auction


## Annoucement

| | |
|---------------------------------|----------------:|
| Term and Type of Security       |     91-Day Bill |
| Security Description            |    13-Week Bill |
| Offering Amount                 | $45,000,000,000 |
| Competitive Bid Rate Increments |          0.005% |
| Maximum Noncompetitive Award    |      $5,000,000 |
| Noncompetitive Closing Time     |   11:00 a.m. ET |
| Competitive Closing Time        |   11:30 a.m. ET |

## Bid Submitted

| Counterparty   | Amount           |  Bid     | Awarded |
|----------------|------------------|----------|---------|
| Counterparty A |      $11,000,000 |   1.550% |         |
| Counterparty B |       $2,000,000 |   1.450% |         |
| Counterparty C |      $12,000,000 |   1.475% |         |
| Counterparty D |      $3,000,000  |   1.565% |         |
| Counterparty E |      $12,000,000 |   1.480% |         |
| Counterparty F |       $1,000,000 |   1.560% |         |
| Counterparty G |      $12,000,000 |   1.485% |         |
| Counterparty H |      $18,000,000 |   1.550% |         |
| Counterparty I |       $2,000,000 |  noncomp |         |
| Counterparty J |      $12,000,000 |   1.355% |         |
| Counterparty K |      $12,000,000 |   1.490% |         |
| Counterparty L |       $7,000,000 |   1.555% |         |
| Counterparty M |       $1,000,000 |  noncomp |         |
| Counterparty N |      $13,000,000 |   1.560% |         |
| Counterparty O |      $12,000,000 |   1.540% |         |
| Counterparty P |      $22,000,000 |   1.530% |         |
| Counterparty Q |      $17,000,000 |   1.555% |         |


* What was the high rate
* How much did each counterparty get allocated?
* What is the coverage ratio?

### Comparison


## Session Info

```{r}
devtools::session_info()
```

```{r}
date()
sessionInfo()
```

```{r}
date()
Sys.getenv()
```


