---
title: "Federal Reserve Mortgage Market Data"
author: "Larry Tentor"
date: "`r (Sys.Date())`"
output:
  html_document:
    df_print: kable
    theme: simplex
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: no
    urlcolor: blue
  pdf_document:
    toc: yes
---

```{r setupExclude, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r setup, include=TRUE}
# List selected libraries
suppressWarnings(library(tidyverse))
suppressWarnings(library(fredr))
```

# Federal Reserve Bank API

You must complete the following steps
  1. Register for a Federal Reserve Bank API key
  2. Create a text file on your local machine. (In windows Explorer > right click > New > Create Document)
  3. Save the file with the name "FRED.key"
  4. Place the key on the first line of the text file and save
  5. Transfer file to lesson05 directory.

```{r}
# Read Federal Reserve Economic Database (FRED) user key
#
# This will need to be configured for each user 
# by signing up for an account at
# https://research.stlouisfed.org/useraccount/apikeys
#
# Then place the api key on the first line of the file FRED.key in the lesson directory.
#
# This key is a long hex number that looks like
#
# ffff231e4928f1f49bb4a3699834d3ca
#
fredFile          <- read.csv('../FRED.key', header = FALSE, sep = ",", dec = ".", stringsAsFactors = FALSE)
GetYourOwnFredKey <- fredFile$V1[1]
fredr_set_key(GetYourOwnFredKey)
```

# Mortgage Debt

### Residential Debt

```{r mortgageDebtResidential}
mortgageDebtResidential <- fredr(
  series_id = "MDOTP1T4FR"
)
mortgageDebtResidential$name <- "Residential"
head(mortgageDebtResidential)

```
Suggested Citation:
Board of Governors of the Federal Reserve System (US), Mortgage Debt Outstanding by Type of Property: One- to Four-Family Residences [MDOTP1T4FR], retrieved from FRED, Federal Reserve Bank of St. Louis; https://fred.stlouisfed.org/series/MDOTP1T4FR, February 8, 2020.  


```{r mortgageDebtResidentialPlot}

ggplot(mortgageDebtResidential, aes(date, value)) + 
  geom_line() + 
  xlab("Date") + 
  ylab("Mortgage Debt [million $]") + 
  ylim(0, ceiling(max(mortgageDebtResidential$value)+0.1)) + 
  ggtitle("History of Mortgage Debt")

```



### Farm Debt

```{r mortgageDebtFarm}
mortgageDebtFarm <- fredr(
  series_id = "MDOTPFP"
)
mortgageDebtFarm$name <- "Farm"
head(mortgageDebtFarm)
```



```{r mortgageDebtFarmPlot}

ggplot(mortgageDebtFarm, aes(date, value)) + 
  geom_line() + 
  xlab("Date") + 
  ylab("Mortgage Debt: Farm [million $]") + 
  ggtitle("History of Mortgage Debt: Farm")


```

Suggested Citation:
Board of Governors of the Federal Reserve System (US), Mortgage Debt Outstanding by Type of Property: Farm [MDOTPFP], retrieved from FRED, Federal Reserve Bank of St. Louis; https://fred.stlouisfed.org/series/MDOTPFP, February 13, 2020.



```{r}

ggplot( ) + 
  geom_line(data = mortgageDebtResidential, aes(date, value), color = "blue") +
  geom_line(data = mortgageDebtFarm, aes(date, value), color = "red") +
  geom_line() + 
  xlab("Date") + 
  ylab("Mortgage Debt [million $]") + 
  ylim(0, ceiling(max(mortgageDebtResidential$value)+0.1)) + 
  ggtitle("History of Mortgage Debt")


```


### Assembly data: Stack

- Can you think of a time you have stacked data

```{r}
#colnames(mortgageDebtResidential)[3] <- 'Residential'
#colnames(mortgageDebtFarm)[3]        <- 'Farm'

# Wide
#mortgageEnhanced <- mortgageDebtResidential %>% inner_join(mortgageDebtFarm, by = c("date"))

#Stacked
mortgageStack    <- rbind(mortgageDebtResidential,mortgageDebtFarm)
head(mortgageStack %>% filter(date == '1995-10-01'))
```
### Assembly data: Wide

- Can you think of a time you have stacked data

```{r}
# Wide
mortgageDebtResidential_              <- mortgageDebtResidential
colnames(mortgageDebtResidential_)[3] <- 'Residential'

mortgageDebtFarm_                     <- mortgageDebtFarm
colnames(mortgageDebtFarm_)[3]        <- 'Farm'

mortgageWide                          <- 
  mortgageDebtResidential_ %>% 
  inner_join(mortgageDebtFarm_, by = c("date"))

head(mortgageWide)

```


### Graph 1995

```{r}

mortgage1995 <- mortgageStack %>% filter(date=='1995-10-01')
mortgage1995

mortgage19952016 <- mortgageStack %>% filter(date=='1995-10-01' | date=='2016-10-01')
mortgage19952016

```

Bar Plot

```{r}

barPlot   <- ggplot(mortgage1995, aes(x="", y=value, fill=name))+
               geom_bar(width = 1, stat = "identity")
barPlot

```


Pie Chart

```{r}

pieChart  <- ggplot(mortgage1995, aes(x="", y=value, fill=name))+
               geom_bar(width = 1, stat = "identity") +
               coord_polar("y", start=0)
pieChart

```

### Graph 1995 & 2016

```{r}

mortgage19952016 <- mortgageStack %>% filter(date=='1995-10-01' | date=='2016-10-01')
mortgage19952016

```

Bar Plot

```{r}

barPlot   <- ggplot(mortgage19952016, aes(x="", y=value, fill=name))+
               geom_bar(width = 1, stat = "identity") +
               facet_wrap( ~ date )
barPlot

```
Pie Chart

```{r}

pieChart  <- ggplot(mortgage19952016, aes(x="", y=value, fill=name))+
               geom_bar(width = 1, stat = "identity", position = position_fill()) +
               coord_polar("y", start=0) +
               facet_wrap( ~ date )
               
pieChart

```


### MultiFamily Debt


```{r mortgageMultiFamily}
mortgageDebtMultiFamily <- fredr(
  series_id = "MDOTPMFR"
)

head(mortgageDebtMultiFamily)
```


Suggested Citation:
Board of Governors of the Federal Reserve System (US), Mortgage Debt Outstanding by Type of Property: Multifamily Residences [MDOTPMFR], retrieved from FRED, Federal Reserve Bank of St. Louis; https://fred.stlouisfed.org/series/MDOTPMFR, February 13, 2020.

