---
title: "Introduction to R and RStudio"
author: "Larry Tentor"
#date:   "`r (Sys.Date())`"
always_allow_html: true
output:
  ioslides_presentation:
#  html_document:
#    toc: true
#    toc_float: true
#    theme: united
#    code_folding: hide
#  html_document:
#    code_folding: hide
#    df_print: kable
#    theme: simplex
#    toc: true
#    urlcolor: blue
#    toc_float:
#      collapsed: false
#      smooth_scroll: false
#output: rmdformats::readthedown
      
---

```{r setupExclude, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(tidyverse)
```


## What is R

Our view for this class

- An interactive environment for doing data science
- A place for repeatable analysis/reproducible research 
    -  https://r4ds.had.co.nz/introduction.html
- [R Project](https://www.r-project.org/about.html)


## RStudio Cloud IDE

Let's start by reviewing the RStudio Cloud Integrated Development Environment (IDE).  An [introduction](https://bookdown.org/ageraci/STAT160Companion/intro.html) is found here.

Positions within IDE 

|        | left      | right      |
|--------|-----------|------------|
| top    |Text Editor|IDE Settings|
| bottom |Console    |R Viewers |

[IDE Cheatsheet](https://rstudio.com/wp-content/uploads/2016/01/rstudio-IDE-cheatsheet.pdf)


## Sample Calculations in the console - 1

### Addition

```{r Addition}
# Addition
105 + 783
```
### Subtraction

```{r Subtration}
# Subtraction
4781 - 832
```

## Sample Calculations in the console - 2

### Multiplication

```{r Multiplication}
# Multiplication
333 * 7
```

### Division $\div$

```{r Division}
# Division
333 / 3
```

## Exercise 01-A.
  [Paired Programming](https://docs.google.com/presentation/d/1E-afLHWmYcTjO0z_hBpAw3AL4Gp4qVQNLOsxP_hq3fI/edit#slide=id.p)
  

## Variables - 1

We can store our intermediate calculations in a storage location.  Atomic storage for numeric, integer, and character.

### my_variable numeric

```{r}
my_variable <- 3 * 7

my_variable
class(my_variable)
```

## Variables - 2

### my_variable integer

```{r}
my_variable <- 3L

my_variable
class(my_variable)
```

## Variables - 3

### my_variable character string

```{r}
my_variable <- "This is a text string"

my_variable
class(my_variable)
```

## Variables - 4

### my_date date type

```{r}
my_variable <- as.Date("1971-03-02")

my_variable
class(my_variable)
```

## Exercise 01-B.
  Switch pairing assignment.


## Loading files
```{r}
my_file <- "../data/DebtTothePenny.csv"

# Help file lines
# ?read.csv
# read.csv(file, header = TRUE, sep = ",", quote = "\"",
#         dec = ".", fill = TRUE, comment.char = "", ...)

DebtTothePenny <- read.csv(my_file, header = TRUE, stringsAsFactors = FALSE)

head(DebtTothePenny)
```

## What is "DebtTothePenny"? 

```{r}
class(DebtTothePenny)
```
Let's look at how to get to specific data elements.

## data.frames - Indicies - Row
```{r}
DebtTothePenny[1,] # Select the first row, all columns
```

## data.frames - Indicies - Row Range and Column
```{r}
DebtTothePenny[1:5,2] # Select the first to fifth row, second column
```
What kind of data is stored in the second column?

## Data Types

```{r}
head(DebtTothePenny$Public.Debt)
```

## Clean up Data Types

Let's create a new dataframe 'Debt' to store the data in desired format.

```{r}
  Debt <- data.frame( date       = as.Date(DebtTothePenny$Effective.Date, "%m/%d/%y")
                    , debtPublic = parse_number(DebtTothePenny$Public.Debt)
                    , debtTotal  = parse_number(DebtTothePenny$Total.Debt))

```

## Data Types

```{r}
 head(Debt)
```

 
 
```{r}
ggplot(Debt, aes(x=date, y=debtTotal)) +
  geom_line() + 
  xlab("Date")
```

## Session Info

```{r}
devtools::session_info()
```

```{r}
date()
sessionInfo()
```



