---
title: "Introduction to R and RStudio"
author: "Larry Tentor"
#date:   "`r (Sys.Date())`"
always_allow_html: true
output:
  ioslides_presentation:
#  html_document:
#    toc: true
#    toc_float: true
#    theme: united
#    code_folding: hide
#  html_document:
#    code_folding: hide
#    df_print: kable
#    theme: simplex
#    toc: true
#    urlcolor: blue
#    toc_float:
#      collapsed: false
#      smooth_scroll: false
#output: rmdformats::readthedown
      
---

```{r setupExclude, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## What is R

Our view for this class

- An interactive environment for doing data science
- A place for repeatable analysis/reproducible research 
    -  https://r4ds.had.co.nz/introduction.html
- [R Project](https://www.r-project.org/about.html)


## RStudio Cloud IDE

Let's start by reviewing the RStudio Cloud Integrated Development Environment (IDE).  An [introduction](https://bookdown.org/ageraci/STAT160Companion/intro.html) is found here.

Positions within IDE 

|        | left      | right      |
|--------|-----------|------------|
| top    |Text Editor|IDE Settings|
| bottom |Console    |R Viewers |

[IDE Cheatsheet](https://rstudio.com/wp-content/uploads/2016/01/rstudio-IDE-cheatsheet.pdf)


## Sample Calculations in the console

### Addition

```{r Addition}
# Addition
105 + 783
```
### Subtraction

```{r Subtration}
# Subtraction
4781 - 832
```

### Multiplication

```{r Multiplication}
# Multiplication
333 * 7
```

### Division $\div$

```{r Division}
# Division
333 / 3
```

## Exercise 01-A.
  Paired Programming.
  

## Variables

We can store our intermediant calculations in a storage location.  Atomic storage for numeric, integer, and character.

### my_variable numeric

```{r}
my_variable <- 3 * 7

my_variable
class(my_variable)
```

### my_variable integer

```{r}
my_variable <- 3L

my_variable
class(my_variable)
```

### my_variable character string

```{r}
my_variable <- "This is a text string"

my_variable
class(my_variable)
```

## Exercise 01-B.
  Switch pairing assignement.

## Session Info

```{r}
devtools::session_info()
```

```{r}
date()
sessionInfo()
```



