---
title: "Exercise 01-D"
author: "(fill in your name)"
output:
  html_document:
    df_print: kable
    theme: simplex
    toc: true
    urlcolor: blue
    toc_float:
      collapsed: false
      smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```

## Specify file

Within RStudio IDE, from the exercise folder go up and look into the data folder.  Find the data file for US 30 year mortgage interest rates and replace "filename.csv" with this.  Capitalization does come into play.

```{r fileLocation}
#my_file <- "../data/filename.csv"
```

## Load


```{r mortgage}
#mortgage <- read.csv(...)

```

## Examine class

Replace "function_name" with the correct name of the function to examine the object type.

```{r}
#function_name(variable_name)

```

## Examine the content of the data.frame

Use either the head function to review the first few rows of the dataset or the tail function to review the last few lines of the dataset.

```{r}
#function_name(variable_name)

```
## Data Manipulation

The DATE field is stored as what data type?

How do we convert it to a date format? And store 

Try ?as.Date


```{r}
#function_name(variable_name)

```

## Plot the mortgage rate

Does this look as you expect?

We will spend additional time on plotting in a follow up session.

```{r}

ggplot(mortgage, aes(x=Date, y=MORTGAGE30US)) +
  geom_line() + 
  xlab("Date")

```





## Session Info

```{r}
devtools::session_info()
```

```{r}
date()
sessionInfo()
```

```{r}
date()
Sys.getenv()
```


