---
title: "Join Examples and Conronovirus Data"
author: "Larry Tentor"
date: "`r (Sys.Date())`"
output:
  html_document:
    df_print: kable
    theme: simplex
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: no
    urlcolor: blue
  pdf_document:
    toc: yes
---

```{r setupExclude, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r setup, include=TRUE}
# List selected libraries
library(tidyverse)
library(usmap)
```

# Focus

The focus of this demo is on how to merge two datasets through operations termed **joins**. These are used for doing lookup tables, in Excel sometimes done using **vlookup/hlookup**.

A simple example would be for state names from state abbreviations.

**Data Table**

| State Code | Electoral Seats |
|------------|-----------------|
| AL         |               9 |
| AK         |               3 |
| AZ         |              11 |
| AR         |               6 |
| CA         |              55 |

**Lookup Table**

| State      | State Code |
|------------|----|
| Alabama    | AL |
| Alaska     | AK |
| Arizona    | AZ |
| Arkansas   | AR |
| California | CA |

We wish to start with the Data Table and get the full state names so these can be displayed in a table for reporting.

# Import

```{r SimpleLoad}

electoralCollege <- read.csv(text="StateCode,Seats
AL,9
AK,3
AZ,11
AR,6
CA,55
CO,9",stringsAsFactors=FALSE)

stateCodeLookup <- read.csv(text="State, StateCode
Alabama,AL
Alaska,AK
Arizona,AZ
Arkansas,AR
California,CA
Delaware,DE",stringsAsFactors=FALSE)

```

# Join Examples

## Inner Join

```{r}
electoralCollege
```

```{r}
stateCodeLookup
```

```{r InnerJoin}
electoralCollegeExtended <- inner_join(electoralCollege, stateCodeLookup)

electoralCollegeExtended
```

```{r InnerJoinwithBy}
electoralCollegeExtended <- inner_join(electoralCollege, stateCodeLookup, by = "StateCode")

electoralCollegeExtended
```
## Inner Join with Different column names

```{r InnerJoinwithDifferentNames}
electoralCollege2 <- electoralCollege
colnames(electoralCollege2)[1] <- "StateId"
electoralCollege2

electoralCollegeExtended2 <- inner_join(electoralCollege2, stateCodeLookup, by = c("StateId" = "StateCode"))

class(c("StateId" = "StateCode"))
electoralCollegeExtended2
```


## Row counts?
- How many rows started in electoral college data set?
- How may rows ended in electoral college extended data set?
 
## Left Join

```{r LeftJoin}
electoralCollegeExtended <- left_join(electoralCollege, stateCodeLookup)

electoralCollegeExtended
```
## Left Join Review

- What changed compared to inner join

## Right Join

```{r RightJoin}
electoralCollegeExtended <- right_join(electoralCollege, stateCodeLookup)

electoralCollegeExtended
```
## Right Join Review

- Is it what you expected?

# Import - Second Case

In this portion we select to load [US population data](https://www.census.gov/data/tables/time-series/demo/popest/2010s-state-total.html) as well as cronovirus reporting data from [Johns Hopkins University Center for Systems Science and Engineering](https://gisanddata.maps.arcgis.com/apps/opsdashboard/index.html#/bda7594740fd40299423467b48e9ecf6).  

```{r PopulationLoad}
dataFile <- '../data/nst-est2019-popchg2010_2019.csv'
population <- read.csv(file=dataFile,stringsAsFactors = FALSE)
```

```{r coronavirusLoad}
# Loop over a number of days and consoldate Corona Virus Data

# This is the base URL for load from the web.
urlBase      <- "https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_daily_reports/"

# Dates selected to load, careful format may change over time
dateSelected <- c(as.Date("2020-03-22"),as.Date("2020-03-23"),as.Date("2020-03-24"))

# Initize empty data
dataStack = c()

# Loops for repeating tasks
for (i in 1:length(dateSelected)) 
  {
    dateSpecified <- dateSelected[i]
    print(paste0("Loading ",format(dateSpecified)))
    
    # Load specified datas file from GitHub web
    dataSpecified <- read.csv(url(paste0(urlBase,format(dateSpecified, "%m-%d-%Y"),".csv")),stringsAsFactors = FALSE)
    dataSpecified$dateFile <- dateSpecified

    # Adjust column name that does not line up with prior files.
    if (colnames(dataSpecified)[1] == "ï..FIPS"){
      colnames(dataSpecified)[1] <- "FIPS"
    }
    if (length(dataStack) == 0)
    {
    dataStack <- dataSpecified
    } else {
    dataStack <- rbind(dataStack,dataSpecified)
    }
  }  
```

# Tidy

## Population Dataset

Simplify dataset to most recent population estimate by State.

```{r}
populationState <-
  population[,c("SUMLEV","STATE","NAME","POPESTIMATE2019")] %>%
  filter(SUMLEV==40)

head(populationState,20)
```

# Analysis

## Daily committed

```{r coronavirusProfile}
 dailyAnalysis <-
  dataStack %>%
    group_by(dateFile) %>%
    summarize(Confirmed=sum(Confirmed)) %>%
    arrange(desc(dateFile))
dailyAnalysis
```

## Coronavirus Profile


```{r}
dataStackUS <-
  dataStack %>%
  filter(Country_Region=="US")

head(dataStackUS)  
```
## US Summary

```{r}

SummaryUS <-
  dataStackUS %>%
  group_by(dateFile, Country_Region) %>%
  summarise(Confirmed=sum(Confirmed), Deaths=sum(Deaths), Recovered=sum(Recovered), Active=sum(Active))

SummaryUS
```

## US State Summary

```{r}
SummaryState <-
  dataStackUS %>%
  group_by(dateFile, Country_Region, Province_State) %>%
  summarise(Confirmed=sum(Confirmed), Deaths=sum(Deaths), Recovered=sum(Recovered), Active=sum(Active))

head(SummaryState,10)
```

## US State Per Capita

```{r}
SummaryStatePer <-
  inner_join(SummaryState,populationState,by= c("Province_State" = "NAME")) %>%
  mutate(ConfirmedPerCapita=Confirmed/POPESTIMATE2019, ConfirmedOneIn = 1/ConfirmedPerCapita) %>%
  filter(dateFile == "2020-03-24") %>%
  arrange(desc(ConfirmedPerCapita), dateFile)

head(SummaryStatePer,10)
```


