---
title:  "SEC Edgar Data"
author: "Larry Tentor"
date:   "`r (Sys.Date())`"
output:
  html_document:
    df_print: kable
    theme: simplex
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: no
    urlcolor: blue
  pdf_document:
    toc: yes
---

```{r setupExclude, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r setup, include=FALSE}
# List selected libraries
library(tidyverse)
library(edgar)
library(XBRL)
# Setting stringsAsFactors = FALSE is recommended to avoid data frames creating factors from character vectors.
options(stringsAsFactors = FALSE)
```

# Focus

The focus of this demo is accessing the data on the SEC EDGAR system.

# CIK Reference

| CIK        | Entity              |
|------------|---------------------|
| 0001652044 | Alphabet, Inc.      |
|      38079 | Sabine Oil Gas Corp |
|    1067701 | United Rentals Inc  |
| 0000854157 | STATE OF WISCONSIN INVESTMENT BOARD |
| 0000919079 | CALIFORNIA PUBLIC EMPLOYEES RETIREMENT SYSTEM |

A company's CIK can be located on the [SEC website](https://www.edgarcompany.sec.gov/servlet/CompanyDBSearch?page=main)

# Entity Filings

Once we have identified an entity we can look over all the filings that they have made for a particular period.


## getFilingInfo

This looks at the filings of a corporate entity.

```{r, echo=TRUE, results='hide'}
filingUnitedRental <- getFilingInfo(1067701, 2006) 
```

```{r}
head(filingUnitedRental)
```

This examines the filings of a pension system.

```{r, echo=TRUE, results='hide'}
filingSWIB <- getFilingInfo(0000854157, c(2016,2017)) 

```

```{r}
head(filingSWIB)
```

## getFilings

This feature downloads the actual entity filings to a local directory.

(.\\Edgar filings_full text\\Form 13F-HR\\854157)

```{r}
SWIB13F <- getFilings(cik.no = 0000854157, c('13F-HR'), c(2016,2017))
```


# Current Report, 8-K

## [8-K Information](https://www.sec.gov/fast-answers/answersform8khtm.html)

This allows us to download the 8-K reports that a company has filed.

In addition to filing annual reports on Form 10-K and quarterly reports on Form 10-Q, public companies must report certain material corporate events on a more current basis. Form 8-K is the “current report” companies must file with the SEC to announce major events that shareholders should know about.
The instructions for Form 8-K describe the types of events that trigger a public company's obligation to file a current report.


```{r 8k-1, echo=TRUE, results='hide'}
# Alphabet Inc. , CIK 0001652044
# Forest Oil Corp, CIK 38079
#output <- get8KItems(cik.no = 38079, filing.year = 2005) ## Returns 8-K events information for CIK '38079' filed in year 2005.
#output <- get8KItems(cik.no = c(1000180,38079), filing.year = c(2005, 2006))
Filing8K <- get8KItems(cik.no = 38079, filing.year = 2015) 
```

```{r 8k-2}
head(Filing8K)
```

# Sentimate Analysis

One area of high research interest is that of text analysis of SEC filings.  This package is also able to examine a basic sentimate analysis.

```{r, echo=TRUE, results='hide'}

senti.df <- getSentiment(cik.no = c('1000180', '38079'), 
                         form.type = '10-K', filing.year = 2006) 
```

```{r}
senti.df
```

# XBRL parsing

```{r, echo=TRUE, results='hide'}
## XBRL instance file to be analyzed, accessed
## directly from SEC website:
inst <- "https://www.sec.gov/Archives/edgar/data/21344/000002134413000050/ko-20130927.xml"
#inst <- "https://www.sec.gov/Archives/edgar/data/854157/000109724120000002/swb13f4q2019.xml"

## Level 1: Function that does all work and returns
## a list of data frames with extracted information:
xbrl.vars <- xbrlDoAll(inst, verbose=TRUE)

```

```{r}

head(xbrl.vars$fact)
#head(xbrl.vars$context)

```

