---
title: "Tidy Examples and Gapminder Review"
author: "Larry Tentor"
date: "`r (Sys.Date())`"
output:
  html_document:
    df_print: kable
    theme: simplex
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: no
    urlcolor: blue
  pdf_document:
    toc: yes
---

```{r setupExclude, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r setup, include=TRUE}
# List selected libraries
library(tidyverse)
library(usmap)
```

# Import

In this recap we select to use a built in dataset that you should have seen during your datacamp experience.

```{r}
library(gapminder)
```

As well as some smaller data sets to illustrate some coding challenges.

```{r sampleDataframe1}
textSample <- 
"MMYYYY, Volatility
 10/2018,29.5
 11/2018,30.1
 12/2019,31.5"
dataframeSample <- read.csv(text = textSample)
```

# Tidy

Since we have selected to use the gapminder dataset we believe it had already been cleansed when creating the dataset for others to use.

## Date conversion MM/YYYY

In this data frame we have the month and year with an associated volatility measure.  Since date variables require a year month and day, how would we convert this text to a date class?

```{r}
dataframeSample$Date1 <- as.Date(dataframeSample$MMYYYY,'%m/%Y')
dataframeSample
```
Well this did not give us what we wanted!

How can we do text processing first so we can use as.Date?  Let's add a day field and set it to the first of the month.

```{r}
dataframeSample$DDMMYYYY <- paste0('01/',trimws(dataframeSample$MMYYYY))
dataframeSample
```

Ok, now we can use this with `as.Date`!

```{r}
dataframeSample$Date2 <- as.Date(dataframeSample$DDMMYYYY,'%d/%m/%Y')
dataframeSample
```

So simplifying all this effort into one statement.

```{r}
dataframeSample$Date3 <- as.Date(paste0('01/',trimws(dataframeSample$MMYYYY)),'%d/%m/%Y')
dataframeSample
```


# Analysis


## Gapminder 1992

```{r}
gapminder1992 <-
  gapminder %>%
  filter(year==1992)
head(gapminder1992)
```

## Gapminder Bubble Chart

```{r gapminderPlot}
# As an exercise try removing different pieces to see what changes!

ggplot(gapminder1992, aes(x=gdpPercap, y=lifeExp, size=pop, color=continent)) +
    geom_point(alpha=0.5) +
    scale_size(range = c(.1, 24), name="Population (M)") + 
    xlab("GDP per Capita") + 
    ylab("Life Expectancy [years]") + 
    ggtitle("1992 gapminder") +
    scale_x_log10()
  
```

## Gapminder Continent Group

```{r}
continentGroup <-
  gapminder1992 %>% 
  group_by(continent) %>% 
  summarize(popSum=sum(as.numeric(pop)),countCountry=n())
continentGroup
```

### Bar Chart

```{r continentGroupBar}
ggplot(continentGroup, aes(x=continent, y=popSum)) +
        geom_bar(stat="identity") +
        xlab("Continent") + ylab("Population") +
        ggtitle("Population by Continent in 1992")
```

### Pie Chart

```{r continentGroupPie}

ggplot(continentGroup, aes(x="", y=popSum, fill=continent)) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y", start=0) +
  theme_void() # remove background, grid, numeric labels

```

## US Population

```{r USPopulation}
head(statepop)
```

```{r USPopulationMap}

plot_usmap(data = statepop, values = "pop_2015", color = "red") + 
  scale_fill_continuous(name = "Population (2015)", label = scales::comma) + 
  theme(legend.position = "right")
```

```{r USPopulationMap2}

plot_usmap(include = c("CA", "ID", "NV", "OR", "WA"), 
  data = statepop, values = "pop_2015", color = "red") + 
  scale_fill_continuous(name = "Population (2015)", label = scales::comma) + 
  theme(legend.position = "right")
```

