---
title: "Homework 01-A Solution"
author: "(fill in your name)"
output:
  html_document:
    df_print: kable
    theme: simplex
    toc: true
    urlcolor: blue
    toc_float:
      collapsed: false
      smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```

## Specify file

In this exercise you will have to download a file from the Federal Reserve Bank and load it.  The rates for fifteen year mortgages are available at https://fred.stlouisfed.org/series/MORTGAGE15US.  Using the "Download" button store this on you computer and then load to RStudio Cloud into the lesson01/data directory


```{r fileLocation}
#my_file <- "../data/filename.csv"
my_file <- "../data/MORTGAGE15US.csv"
```

## Load


```{r mortgage}
#mortgage <- read.csv(...)

mortgage <- read.csv(my_file, header = TRUE, stringsAsFactors = FALSE)

```

## Examine class

Replace "function_name" with the correct name of the function to examine the object type.

```{r}
#function_name(variable_name)
class(mortgage)
```

## Examine the content of the data.frame

Use either the head function to review the first few rows of the dataset or the tail function to review the last few lines of the dataset.

```{r}
#function_name(variable_name)
head(mortgage)

```
## Data Manipulation

The DATE field is stored as what data type?

How do we convert it to a date format? And store 

Try ?as.Date


```{r}
#function_name(variable_name)
mortgage$Date <- as.Date(mortgage$DATE,'%m/%d/%Y')

```

## Plot the mortgage rate

Does this look as you expect?

Include a comment on the comparison of the 15 year rates to the 30 year rates ploted in Exercise D.

<<Insert Answer here>>

Submit the single html file "homework01-A.html", Blackboard may require that you zip it prior to submission.

```{r}
ggplot(mortgage, aes(x=Date, y=MORTGAGE15US)) +
  geom_line() + 
  xlab("Date")

```





## Session Info

```{r}
devtools::session_info()
```

```{r}
date()
sessionInfo()
```

```{r}
date()
Sys.getenv()
```


